WunderPass-White-Paper

### 2022-01-31 [Einleitung].tex
Ausformulieren des Kapitel "Einleitung".
REFACTORING

% !TEX root = paper.tex
\section{Einleitung}
\label{sec:einleitung}
\todo{TODO}
Hallo!

>>>>

% !TEX root = paper.tex
\section{Einleitung}
\label{sec:einleitung}

\input{C:/Users/Slava/White-Paper/[02][Einleitung]/[Einleitung][Identität]}    % binde die Datei '[Einleitung][Identität].tex' ein
\input{C:/Users/Slava/White-Paper/[02][Einleitung]/[Einleitung][digitale Identität]}    % binde die Datei '[Einleitung][digitale Identität].tex' ein
\input{C:/Users/Slava/White-Paper/[02][Einleitung]/[Einleitung][Probleme]}    % binde die Datei '[Einleitung][Probleme].tex' ein

\vspace{0.5cm}
